\chapter{Robust Stabilization of Double Integrator System}  

Robust finite-time stabilization is often treated under the analytical framework of homogeneity and has been frequently illustrated in the context of the feedback control of the double integrator. 
For such a simple system, the simplest considered robust finite-time controller is the `twisting' controller composed of the signum value of position error and velocity error.
Here, a controller with linear component of velocity error and signum component of position error is discussed.
The analytical findings are further illustrated through computer simulations.

\section{从合围问题中引发的单体问题}

\subsection{First Order}

\begin{proposition}
    For a function $\phi(s):\RR^n\to\RR^n$ with $\phi^T(s)(x-x^*)<0$, $\forall \|s-x^*\|\leq \|x-x^*\|$ and $\phi(x^*)$
\end{proposition}

\begin{equation}
    \dot{x}=\phi(x)=-x+\frac{1}{x}
\end{equation}

\begin{equation}
    V=\frac{1}{2}v^2-\int_{x^*}^x \phi(s) ds
\end{equation}


\begin{equation}
    \dot{V}=vu-(\phi(x)-\phi(x^*))v
    =-v^2
\end{equation}

\subsection{Second Order}

\begin{equation}
    \ddot{x}=\phi(x)-k\dot{x}=-x+\frac{1}{x}-k\dot{x}
\end{equation}

\begin{equation}
    V=\frac{1}{2}v^2-\int_{x^*}^x \phi(s) ds
\end{equation}


\begin{equation}
    \dot{V}=vu-(\phi(x)-\phi(x^*))v
    =-v^2
\end{equation}



\section{Introduction}

Consider the double integrator system, expressed as
\begin{equation}\label{eq:model}
    \begin{cases}
        \dot{x}=v,\\
        \dot{v}=u+\delta,
    \end{cases}
\end{equation}
where $\delta$ is perturbation with $\vert \delta \vert \leq C$.

The system \eqref{eq:model} can be stabilized robustly with a twisting controller with 
\begin{equation}
    u=-k_1 \sign(x) -k_2 \sign(v),
\end{equation}
under the parameter $k_1>k_2>C$.
\cite[Theorem 4.1]{shtesselSlidingModeControl2014} proves this with geometrical method.
\cite[Theorem 4.1]{orlovFiniteTimeStability2004} proves this with Lyapunov method.

\cite[Theorem 4.2]{orlovFiniteTimeStability2004} also shows that the system can also be stabilized with 
\begin{equation}
    u=-k_1 \sign x -k_2 \sign v -k_3 x -k_4 v,
\end{equation}
where $0<C<k_2<k_1-M$ and $k_3\geq 0,k_4 \geq 0$.

If no perturbation in this system, many controllers can be used.
The simplest controller is a linear feedback controller $u=-k_1 x -k_2 v$ 
with exponential convergence.
As proved in \cite[Theorem 3.1]{zavala-rioContinuousFinitetimeStabilization2022},
the system \eqref{eq:model} with $C=0$ can be stabilized with a homogeneous controller
\begin{equation}
    u=-k_1 \sign(x)|x|^{a_1}-k_2 \sign(v)|v|^{a_2},
\end{equation}
where $k_1>0,k_2>0$ and $0<a_1<a_2<1$.
This controller guarantees finite-time convergence.

\section{Main Result}

We found the following controller can also robustly stabilize this system with only one $\sign$ function
\begin{equation}\label{eq:-signx-v}
    u=-k_1 \sign x -k_2 v.
\end{equation}

\begin{theorem}
    The double integrator can be robustly stabilized with the controller \eqref{eq:-signx-v}
    with $k_1 k_2 >C$.
\end{theorem}
\begin{proof}
    Select $V=k_1|x|+\frac{1}{2}|v|^2$, we have 
    \begin{equation*}
        \dot{V}=\sign(x) v + v (u+\delta)=
        v(k_1\sign(x)-k_1 \sign(x)-k_2 v +\delta)
        \leq -|v|(k_2|v|-C).
    \end{equation*}
    Then $\{|v|\leq \frac{C}{k_2}\}$ is a positive invariance set.
    In this set, 
    \begin{equation*}
        \ddot{x}=-k_1 \sign x -k_2 \dot{x} +\delta
    \end{equation*}
    Since $k_1>2C$, 
    \begin{equation*}
        \ddot{x} {x}<0
    \end{equation*}
\end{proof}

\section{Discussion}

extend to higher order system?

 
  
